XXX TITLE

### 2021-02-18 submission/TOPML_Workshop/paper.tex
TOPML updated

%%%%%%%% ICML 2021 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

@@

\newcommand{\michael}[1]{{\color{red}\sf{[Michael: #1]}}}

@@

>>>>

@@

\newcommand{\michael}[1]{{\color{red}\sf{[Michael: #1]}}}
\newcommand{\charles}[1]{{\color{blue}\sf{[Charles: #1]}}}

@@

\charles{We apply our theory of Heavy Tailed Self-Regularization (HTSR) to predict the generalization accuracies of the pre-trained models provided in this contest, as a function of both model depth (L) and the solver hyperparameters (batch size, dropout, weight decay), and compare quality metrics that describe both the heavy-tailed shape and norm-based scale of the model layer weight matrices.  In doing so, we identify what amounts to a Simpson’s paradox, in which
shape and scale metrics show opposite behavior, and a combine metric resolves the paradox}

\begin{figure}[t!] 
    \centering
    \subfigure[Spectral Norm $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$]{
      \includegraphics[width=4.0cm]{img/simpsons-task2-logspectralnorm.png}
    }
    \subfigure[Alpha Hat $\hat{\alpha}$]{
     \includegraphics[width=4cm]{img/simpsons-task2-alpha_weighted.png}
    }
    \caption{Test accuracy as a function of the
Log Spectral Norm $\log\Vert\mathbf{W}\Vert_{\infty}$ 
and the HTSR Alpha Hat $\hat{\alpha}$ metrics
as model hyperparameters and depth are varied. 
Models from the NeurIPS Predicting Generalization contest.}
    \label{fig:simpsons}
\end{figure}
